---
title: "bike"
author: "Anonymous"
date: "12/4/2020"
output:
   pdf_document:
     toc: yes
     toc_depth: 1
     latex_engine: xelatex
---


# load library
```{r results = "hide", message = FALSE}
# load packages
#library(aaltobda)
library(rstan)
library(ggplot2)
library(tidyr) 
library(dplyr)
library("bayesplot")
library(grid)
library(brms)
library(loo)
library(weathermetrics)
# load data
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```




##  Preprocesing data
```{r}

bikes_raw <- read.csv("bike.csv", header=T, stringsAsFactors=F)

#bike <- head(bike, 100) # select on 100 records to ease computing
#bike <- transform(bike, Total=as.numeric(Total))

bikes <- data.frame(bikes_raw[c('Day','High.Temp...F.','Low.Temp...F.', 'Precipitation','Manhattan.Bridge')])

# remove "," in count character type
bikes$Manhattan.Bridge <- gsub(",","",bikes$Manhattan.Bridge)

# change F -> Celsius degree 
bikes$High.Temp...F. <- fahrenheit.to.celsius(bikes$High.Temp...F., 2)
bikes$Low.Temp...F. <- fahrenheit.to.celsius(bikes$Low.Temp...F., 2)

names(bikes) <- c('weekday','hightemp','lowtemp','precip','Mah_count')
bikes <- transform(bikes, Mah_count=as.numeric(Mah_count))

bikes <- head(bikes, 100)

head(bikes)

na.zero <- function (x) {
    x[is.na(x)] <- 0
    return(x)
}

get.snow <- function(x) {
  result <- 0
  if (grepl('(S)',x)){
    result <- as.double(gsub("[^0-9.-]", "", x))
  }
  return(result)
}

mah_bikes <- within(bikes, precip_rain<-as.double(precip))

#bikes$precip_rain <- as.double(bikes$precip)

# subtitute na by zero
mah_bikes$precip_rain <- na.zero(mah_bikes$precip_rain)

# return S (snow) with value and create new column from precipation
mah_bikes$precip_snow <- lapply(mah_bikes$precip, get.snow)
mah_bikes$precip_snow <- as.numeric(mah_bikes$precip_snow)

mah_bikes <- data.frame(mah_bikes[c('weekday','hightemp','lowtemp','precip_rain','precip_snow','Mah_count')])

# convert weekday to categorical variables.
mah_bikes$weekday <- as.factor(mah_bikes$weekday)
head(mah_bikes)

```

## Plot observation
```{r}

# plot scatter
ggplot() +
  geom_point(aes(weekday, Mah_count), data = mah_bikes, size = 1) +
  labs(y = "Bikes", x= "week day", title ="Bycicle cross Mahattan by day") +
  theme(plot.title = element_text(hjust = 0.5)) +
  guides(linetype = F)

# with smooth line
#plot(covid_linear$Week, covid_linear$Cases, main="Covid cases by week and smooth line", xlab="Week", ylab="Cases")
#with(covid_linear, lines(lowess(covid_linear$Cases~covid_linear$Week)))

```

## saving processed data
```{r}
write.csv(mah_bikes, "mah_bike_counts.csv", row.names = F)
```


## plot boxplot
```{r}
library(MASS)
mah_bikes$weekday <- factor(mah_bikes$weekday, levels=c('Sunday', 'Monday','Tuesday','Wednesday','Thursday','Friday','Saturday'))
boxplot(count~weekday, xlab="Weekday", ylab="Count", data=mah_bikes)
```

# quantitative varaible
```{r}
mah_bikes_quant=data.frame(mah_bikes[c('hightemp','lowtemp','precip_rain','precip_snow','Mah_count')])
plot(mah_bikes_quant)
```
# Fit by standard linear regression, it will not be a good fit, but for comparision
```{r results = "hide", message = FALSE}
fit1 <- brm(Mah_count ~ .,
                     family = gaussian(),
                     data = mah_bikes,
                     prior = c(set_prior("normal(0,1000)", class="Intercept"),
                               set_prior("inv_chi_square(0.1)", class="sigma")),
                     )
summary(fit1)
```
## stan model 1
```{r}
sm1 <- make_stancode(Mah_count ~ .,
                     family = gaussian(),
                     data = mah_bikes,
                     prior = c(set_prior("normal(0,1000)", class="Intercept"),
                               set_prior("inv_chi_square(0.1)", class="sigma")),
                     )

sm1
```
# Analyze posterior
```{r}
mcmc_areas(as.matrix(fit1), prob_outer = .999)
```

## predictive check
```{r}
loo1 <- loo(fit1)
plot(loo1)
pp_check(fit1,nsamples = 59)
```
# predict responses based on the fitted model
```{r}
head(predict(fit1))
```

# plot conditional effects for each predictor
```{r}
plot(conditional_effects(fit1), ask = FALSE)
```

# Plot the MCMC chains and posterior distribution
```{r}
plot(fit1)
```

# Fit linear poisson for mahattance bridge count
```{r results = "hide", message = FALSE}

fit2 <- brm(Mah_count ~ .,
                     family = poisson(link=log),
                     data = mah_bikes,
                     #prior = c(set_prior("normal(0,10)", class="Intercept"), # doesn't work well
                    #           set_prior("inv_chi_square(0.1)", class="b")), # doesn' work well
                     prior = c(set_prior("normal(0,10)", class="Intercept"), # doesn't work well
                               set_prior("normal(0,10)", class="b")), # doesn' work well
                     )
summary(fit2)

```

## stancode 
```{r}
#get_prior(Mah_count ~ .,family = poisson(link=log),data = mah_bikes)

sm2 <- make_stancode(Mah_count ~ .,
                     family = poisson(link=log),
                     data = mah_bikes,
                     #prior = c(set_prior("normal(1000,2000)", class="Intercept"),
                    #           set_prior("normal(0,2)", class="b")),
                     )

sm2
```

## Analyze posterior
```{r}
mcmc_areas(as.matrix(fit2), prob_outer = .999)
```

## predictive check
```{r}
loo(fit2)
pp_check(fit2,nsamples = 20)
```

## predict responses based on the fitted model
```{r}
head(predict(fit1))
```

## plot conditional effects for each predictor
```{r}
plot(conditional_effects(fit1), ask = FALSE)
```

## Plot the MCMC chains and posterior distribution
```{r}
plot(fit1)
```

# Fit Gaussian Process for mahattance bridge count
```{r results = "hide", message = FALSE}

fit2 <- brm(Mah_count ~ gp(.),
                     family = poisson(link=log),
                     data = mah_bikes,
                     prior = c(set_prior("normal(0,10)", class="Intercept"),
                               set_prior("inv_chi_square(0.1)", class="b")),
                     )
summary(fit2)

```

## stancode 
```{r}
get_prior(Mah_count ~ .,family = poisson(link=log),data = mah_bikes)

sm2 <- make_stancode(Mah_count ~ .,
                     family = poisson(link=log),
                     data = mah_bikes,
                     prior = c(set_prior("normal(1000,2000)", class="Intercept"),
                               set_prior("normal(0,2)", class="b")),
                     )

sm2
```

## Analyze posterior
```{r}
mcmc_areas(as.matrix(fit2), prob_outer = .999)
```

## predictive check
```{r}
loo(fit2)
pp_check(fit2,nsamples = 20)
```

## predict responses based on the fitted model
```{r}
head(predict(fit1))
```

## plot conditional effects for each predictor
```{r}
plot(conditional_effects(fit1), ask = FALSE)
```

## Plot the MCMC chains and posterior distribution
```{r}
plot(fit1)
```

